---
title: "UAE Cognitive Funcintion Paper 2"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='UAE_CogPaper_Figs/fig-', echo=FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(lubridate)
library(reshape2)
library(stats)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)
library(ggplot2)
library(ggridges)
library(lme4)
library(lmerTest)
library(EZ2)

source('functions.R')
```

```{r load_scripts, echo=FALSE, results='asis'}
source('1_CogPaper_DataOrg.R')
source('2_CogPaper_tablesWeightStatus.R')
source('3_CogPaper_analyses.R')
source('4_CogPaper_figs.R')
```

\clearpage

# Measurement of Weight Status

We decided to use the International Obesity Task Force (IOTF) designation of weight status for the sample. They use smoothed, sex-specific BMI curves meant to match the the BMI cutoffs for overweight (OW; 25 $kg/m^2$) and obesity (OB; 30 $kg/m^2$) at age 18 yrs.

Rather than BMI-zscore or BMI-percentile, we chose to use percent of overweight cutoff because recent studies shows it has a tighter association with measured adiposity:

BMI $\%$ of overweight = $\frac{child BMI}{BMI\: at\: age-\: and\: sex-\: adjusted\: overweight\: cutoff}*100$

<100 $\%$ - indicates child BMI is below the overweight cutoff for age and sex (i.e., has healthy weight)
100 $\%$ - indicates child BMI is the same as the overweight cutoff for age and sex
>100 $\%$ - indicates child BMI is above the overweight cutoff for age and sex (i.e., has overweight or obesity)

\FloatBarrier

```{r pOW_DensityPlot, echo=FALSE, include = TRUE}
pOW_plot
```

Density plot of percent of overweight by sex. The shaded regions indicated those with healthy weight (blue), overweight (yellow), and obesity (red). The points show denisity of participants by sex (purple circles = female, orange triangles = males).

\FloatBarrier
\clearpage

# Participant Characteristics

```{r Demo_sex_tab, echo=FALSE, results='asis'}
as_kable_extra(demo_tab_merge, caption = 'Demographic Characteristics by Sex', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

```{r Demo_OB_tab, echo=FALSE, results='asis'}
as_kable_extra(UAE_demo_OB_stat, caption = 'Demographic Characteristics by Weight Status', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage
  
## Associations between Demographics and Percent of Overweight Cutoff

### t-test for sex
```{r pOW_sex_ttest, echo=FALSE, results='verbatim'}
pOW.sex_ttest
```

### Correlation Matrix

```{r pOW_demo_cors, echo=FALSE, results='asis'}
kable(pOW_demo_cormat, "latex",  digits = 3, caption = "Correlations between percent of overweight cuttoff and demographic characteristics", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

```{r pOW_demo_cormat_ps, echo=FALSE, results='asis'}
kable(pOW_demo_cormat_ps, "latex",  digits = 3, caption = "P-vales for the correlations between percent of overweight cuttoff and demographic characteristics", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Only child age was associated with percent of overweight cutoff - older children tended to have higher percent of overweight cutoff indicating older children were more likely to have overweight or obesity. There was no association with father or mother education level, which differs from finding in the US. Hip to waist ratio was also not associated with percent of overweight cutoff.

\FloatBarrier

### One-Way ANOVA for Income Categories

```{r pOW_income_anova, echo=FALSE, results='verbatim'}
pOW_income_anova
```

\FloatBarrier

There was no difference in percent of overweight by monthly income category. 

\FloatBarrier

### Sensitivity Tests

```{r pOW_age_mod, echo=FALSE, results='asis'}
kable(IOTF_age_pOWcutoff_tab, digits = 3, caption = "Linear Model: pOWcutoff - SES category + Maternal Education + Age + Sex", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

After controlling for family income, mother education, and child sex, child age was significantly associated with percent of overweight such that for each year older, the expected percent of overweight is predicted to increase 4.24% points.

\FloatBarrier
\clearpage

# Neuropsychological Assessments 

```{r neuropsych_sex_tab, echo=FALSE, results='asis'}
as_kable_extra(neuropsych_tab_merge, caption = 'Neuropsychological Performance by Sex Status', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier

Percent of overweight and height:weight ratio were not associated with any of the neuropsychological assessments. Number of comorbidities was associated with total digit span SS such that the higher number of comorbidities the lower the standard score.

\FloatBarrier
\clearpage

```{r neuropsych_OB_tab, echo=FALSE, results='asis'}
as_kable_extra(UAE_neuropsych_OBstat, caption = 'Neuropsychological Performance by Weight Status', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier
Performance on neuropsychological assessments did not differ by weight status. There were 5 people who had Performance IQ < 70 so all results are presented with and without those 5. Likely the PRI < 70 was due in part to attention/engagement and may not accurately reflect PRI.

\FloatBarrier
\clearpage

## Correlation Matrix

```{r pOW_neuropsych_cor, echo=FALSE, results='asis'}
kable(neuropsych_cormat, digits = 3, caption = "Correlations between neuropsychological performance and percent of overweight", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_neuropsych_corps, echo=FALSE, results='asis'}
kable(neuropsych_cormat_ps, digits = 3, caption = "Correlation p values between neuropsychological performance and percent of overweight ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Percent of overweight and height:weight ratio were not associated with any of the neuropsychological assessments. Number of comorbidities was associated with total digit span SS such that the higher number of comorbidities the lower the standard score.

\FloatBarrier

## Correlation Matrix - IQ >= 70

```{r pOW_neuropsych_IQ70_cor, echo=FALSE, results='asis'}
kable(neuropsych_IQ70_cormat, digits = 3, caption = "Correlations between neuropsychological performance and percent of overweight", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_neuropsych_IQ70_corps, echo=FALSE, results='asis'}
kable(neuropsych_IQ70_cormat_ps, digits = 3, caption = "Correlation p values between neuropsychological performance and percent of overweight ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

After exculding the 5 participants with IQ < 70, percent of overweight and height:weight ratio were not associated with any of the neuropsychological assessments. Number of comorbidities was still associated with total digit span SS such that the higher number of comorbidities the lower the standard score. After excluding the 5 participants, greater number of comorbidities was also associated with lower Block T-scores and backward digit span SS.

\FloatBarrier
\clearpage

## WASI - Block
\FloatBarrier
```{r pOW_block_fig, echo=FALSE, include = TRUE}
pOW_BlockT_plot
```

\FloatBarrier

```{r pOW_block_modtest, echo=FALSE}
anova(pOW_BlockT_mod, pOW_BlockT_quadmod)
```

\FloatBarrier

After looking at the association between Block T-score and percent of overweight, a non-linear association was suspected. Adding a quadratic term to the model significantly improved model fit.

\FloatBarrier

```{r pOW_block_mod, echo=FALSE, results='asis'}
kable(pOW_BlockT_quad_sum$coefficients, digits = 3, caption = "WASI Block model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

After controlling for income, maternal education, age, and sex, there was a significant quadratic effect of percent of overweight on Block performance. The linear association between percent of overweight and performance becomes less positive as percent of overweight increases such that the slope changes from positive to negative at 131% of overweight cutoff. This indicates that both performance is worse in those with both low and height weight for their age and sex. Additionally, those whose families made >\$75,000 AED had Block T-Scores that were 8 point higher than those whose families made between \$25,000-\$55,000 AED.

\FloatBarrier

```{r pOW_IQ70_block_mod, echo=FALSE, results='asis'}
kable(pOW_BlockT_IQ70_quad_sum$coefficients, digits = 3, caption = "WASI Block model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Pattern of results remained unchanged when restricting to IQ >=70 with just a little loss in significance due to lower participant numbers.

\FloatBarrier
```{r pOW_IQ70block_fig, echo=FALSE, include = TRUE}
pOW_IQ70_BlockT_plot
```

\FloatBarrier
\clearpage

## WASI - Matrix

```{r pOW_matrix_fig, echo=FALSE, include = TRUE}
pOW_MatrixT_plot
```

\FloatBarrier

The model for Matrix performance was not improved by adding a quadratic term. 

```{r pOW_matrix_modtest, echo=FALSE}
anova(pOW_MatrixT_mod, pOW_MatrixT_quadmod)
```

\FloatBarrier

```{r pOW_matrix_mod, echo=FALSE, results='asis'}
kable(pOW_MatrixT_sum$coefficients, digits = 3, caption = "WASI Matrix model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Matrix performance was not associated with percent of overweight. There was, however, a difference by income such that those whose families made >\$75,000 AED had Matrix T-Scores that were 9 points higher than those whose families made between \$25,000-\$55,000 AED.

\FloatBarrier

```{r pOW_IQ70_matrix_mod, echo=FALSE, results='asis'}
kable(pOW_MatrixT_IQ70_sum$coefficients, digits = 3, caption = "WASI Matrix model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier
```{r pOW_IQ70matrix_fig, echo=FALSE, include = TRUE}
pOW_IQ70_MatrixT_plot
```

\FloatBarrier
\clearpage

## WASI - PRI

```{r pOW_PRI_modtest, echo=FALSE}
anova(pOW_PRI_mod, pOW_PRI_quadmod)
```
\FloatBarrier

There is a trend for a quadratic term improving the model fit.

\FloatBarrier

```{r pOW_PRI_mod, echo=FALSE, results='asis'}
kable(pOW_PRI_quad_sum$coefficients, digits = 3, caption = "WASI PRI model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

<!-- ```{r pOW_IQ70_PRI_mod, echo=FALSE, results='asis'} -->
<!-- kable(pOW_PRI_IQ70_quad_sum$coefficients, digits = 3, caption = "WASI PRI model - IQ >= 70", booktabs=TRUE)  %>% -->
<!--   kable_styling(latex_opticons = c("hold_position", "repeat_header")) -->
<!-- ``` -->
<!-- \FloatBarrier -->


\clearpage

## Digit Span - Forward
\FloatBarrier
```{r pOW_dsforward_fig, echo=FALSE, include = TRUE}
pOW_DSforward_plot
```

\FloatBarrier
```{r pOW_dsforward_mod, echo=FALSE, results='asis'}
kable(pOW_dsforward_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was no association with percent of overweight or any other demographic variable.

\FloatBarrier
```{r pOW_IQ70_dsforward_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsforward_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Sleep
\FloatBarrier
```{r pOW_dsforward_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_dsforward_sleep_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model - Sleep Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was no interaction with percent of overweight.

\FloatBarrier
```{r pOW_IQ70_dsforward_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsforward_sleep_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model - Sleep Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### SDQ
\FloatBarrier
```{r pOW_dsforward_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_dsforward_SDQ_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model - SDQ Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_dsforward_SDQ_slopes, echo=FALSE, results='asis'}
kable(test(pOW_dsforward_SDQ_slopes), digits = 3, caption = "Digist Span Forward SS model - SDQ Interaction - simple slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was a trend for an interaction between SDQ total problems and %IOTF-25 such that the association between %IOTF-25 and Digit Span Forward became more negative with increasing problems reported. However, despite becoming more negative, the association between %IOTF-25 and Digit Span Forward was not significant when looking at SDQ scores 1 SD above or below the mean.

\FloatBarrier
```{r pOW_IQ70_dsforward_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsforward_SDQ_sum$coefficients, digits = 3, caption = "Digist Span Forward SS model - SDQ Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

\clearpage

## Digit Span - Backward
\FloatBarrier
```{r pOW_dsbackward_fig, echo=FALSE, include = TRUE}
pOW_DSbackward_plot
```

\FloatBarrier
```{r pOW_dsbackward_mod, echo=FALSE, results='asis'}
kable(pOW_dsbackward_sum$coefficients, digits = 3, caption = "Digist Span Backward SS model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
There was no association with percent of overweight. There was, however, an association with age such that older children tended to have lower standard scores than younger children. Males also had a trend level lower performance than females.

\FloatBarrier
```{r pOW_IQ70_dsbackward_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsbackward_sum$coefficients, digits = 3, caption = "Digist Span Backward SS model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Sleep
\FloatBarrier
```{r pOW_dsbackward_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_dsbackward_sleep_sum$coefficients, digits = 3, caption = "Digit Span Backward SS model - Sleep Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was no interaction with percent of overweight.

\FloatBarrier
```{r pOW_IQ70_dsbackward_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsbackward_sleep_sum$coefficients, digits = 3, caption = "Digit Span Backward SS model - Sleep Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### SDQ
\FloatBarrier
```{r pOW_dsbackward_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_dsbackward_SDQ_sum$coefficients, digits = 3, caption = "Digit Span Backward SS model - SDQ Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was no interaction with percent of overweight.

\FloatBarrier
```{r pOW_IQ70_dsbackward_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dsbackward_SDQ_sum$coefficients, digits = 3, caption = "Digit Span Backward SS model - SDQ Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier
\clearpage

## Digit Span - Total
```{r pOW_dstotal_mod, echo=FALSE, results='asis'}
kable(pOW_dstotal_sum$coefficients, digits = 3, caption = "Digist Span Total SS model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_IQ70_dstotal_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_dstotal_sum$coefficients, digits = 3, caption = "Digist Span Total SS model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
\clearpage

## Coding
\FloatBarrier
```{r pOW_coding_fig, echo=FALSE, include = TRUE}
pOW_coding_plot
```

\FloatBarrier
```{r pOW_coding_mod, echo=FALSE, results='asis'}
kable(pOW_coding_sum$coefficients, digits = 3, caption = "Coding SS model", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
There was no association with percent of overweight. There was, however, an association with age such that older children had lower SS compared to younger children.

\FloatBarrier

```{r pOW_IQ70_coding_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_coding_sum$coefficients, digits = 3, caption = "Coding SS model - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Sleep
\FloatBarrier
```{r pOW_coding_sleep_fig, echo=FALSE, include = TRUE}
pOW_sleep_coding_plot
```

\FloatBarrier
```{r pOW_coding_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_coding_sleep_sum$coefficients, digits = 3, caption = "Coding SS model - Sleep Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier


```{r pOW_coding_sleep_slopes, echo=FALSE, results='asis'}
kable(test(pOW_coding_sleep_slopes), digits = 3, caption = "Coding SS model - Sleep Interaction - Simple Slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was an trend for an interaction between sleep and %IOTF-25 such that the association between %IOTF-25 and coding became more negative with higher CSHQ total scores. At CSHQ total scores 1 SD above the mean, the association between %IOTF-25 was significant such that higher weight status was associated with slower cogntive processing speed. 

\FloatBarrier
```{r pOW_IQ70_coding_sleep_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_coding_sleep_sum$coefficients, digits = 3, caption = "Coding SS model - Sleep Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier
\clearpage

### SDQ
\FloatBarrier
```{r pOW_coding_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_coding_SDQ_sum$coefficients, digits = 3, caption = "Coding SS model - SDQ Interaction", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

There was no interaction with percent of overweight.

\FloatBarrier
```{r pOW_IQ70_coding_SDQ_mod, echo=FALSE, results='asis'}
kable(pOW_IQ70_coding_SDQ_sum$coefficients, digits = 3, caption = "Coding SS model - SDQ Interaction - IQ >= 70", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier
\clearpage

# Nback
\FloatBarrier
```{r nback_tab, echo=FALSE, results='asis'}
as_kable_extra(UAE_nback_tab, caption = 'Nback Performance by Sex Status', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

```{r nback_OB_tab, echo=FALSE, results='asis'}
as_kable_extra(UAE_nback_OBstat, caption = 'Nback Performance by Weight Status', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```
\FloatBarrier

There was a trend for children with HW to have lower percent correct hits and ballanced accuracy during 1-back compared to those with overweight or obesity. There was a significant effect for 1-back Percent Hits such that those with HW showed lower sensitivity. May be due to those with lower weights being included in the HW category as <85th percentile.

\FloatBarrier
\clearpage

### Correlation Matrix

```{r pOW_nback_cor, echo=FALSE, results='asis'}
kable(nback_cormat, digits = 3, caption = "Correlations between Nback performance and percent of overweight", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_nback_corps, echo=FALSE, results='asis'}
kable(nback_cormat_ps, digits = 3, caption = "Correlation p values between Nback performance and percent of overweight ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

Percent of overweight was positively correlated with 1-back Percent Hits sensitivity.

\FloatBarrier

### Correlation Matrix - IQ >= 70

```{r pOW_nback_IQ70_cor, echo=FALSE, results='asis'}
kable(nback_IQ70_cormat, digits = 3, caption = "Correlations between neuropsychological performance and percent of overweight", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

```{r pOW_nback_IQ70_corps, echo=FALSE, results='asis'}
kable(nback_IQ70_cormat_ps, digits = 3, caption = "Correlation p values between neuropsychological performance and percent of overweight ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```
\FloatBarrier

After excluding those with performance IQ < 70, percent of overweight was positively correlated with both 1-back Percent Hits sensitivity and ballanced accuracy.

## Nback - Load x Percent of Overweigth

### Ballanced Accuracy

\FloatBarrier
```{r pOW_balacc_fig, echo=FALSE, include = TRUE}
pOW_Nback_plot
```
\FloatBarrier

```{r pOW_balacc_block_mod, echo=FALSE, results='asis'}
kable(pOW_BalAccInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: Ballanced Accuracy", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
There was no interaction and no main effect of percent of overweight. There was a significant effect of Load with better ballanced accuracy in 1- than 2-back. Age was positively associated with ballanced accuracy overall.

\FloatBarrier

```{r pOW_IQ70_balacc_block_mod, echo=FALSE, results='asis'}
kable(pOW_IQg70_BalAccInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: Ballanced Accuracy - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### False Alarms
```{r pOW_FA_block_mod, echo=FALSE, results='asis'}
kable(pOW_pFAInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: False Alarms", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

There was no interaction and no main effect of percent of overweight. There was a significant effect of Load with lower false alarm percentage in 1- than 2-back. Age was negatively associated with false alarm percentage overall.

\FloatBarrier

```{r pOW_IQ70_balacc_FA_mod, echo=FALSE, results='asis'}
kable(pOW_IQg70_pFAInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Percent Hits
\FloatBarrier

```{r pOW_phits_block_mod, echo=FALSE, results='asis'}
kable(pOW_phits_anova, digits = 3, caption = "Nback Load x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
There was no interaction and no main effect of percent of overweight. There was a significant effect of Load with better Percent Hits in 1- than 2-back. Age was positively associated with Percent Hits overall.

\FloatBarrier

```{r pOW_IQ70_phits_block_mod, echo=FALSE, results='asis'}
kable(pOW_IQg70_phits_anova, digits = 3, caption = "Nback Load x Percent of Overweight: Percent Hits - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### RT
\FloatBarrier

```{r pOW_rt_block_mod, echo=FALSE, results='asis'}
kable(pOW_meanRTInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: mean RT", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
There was no interaction and no main effect of percent of overweight. There was a significant effect of Load with better mean RT in 1- than 2-back. Age was positively associated with mean RT overall.

\FloatBarrier

```{r pOW_IQ70_rt_block_mod, echo=FALSE, results='asis'}
kable(pOW_IQg70_meanRTInt_anova, digits = 3, caption = "Nback Load x Percent of Overweight: mean RT - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

## Nback: Percent of Overweight x N Comorbidities

### Balanced Accuracy

\FloatBarrier
```{r pOW_ncomorbid_balacc_fig, echo=FALSE, include = TRUE}
pOW_ncomorbid_BalAcc_plot
```
\FloatBarrier

```{r pOW_ncomorbid_balacc_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_BalAccInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Ballanced Accuracy", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r pOW_ncomorbid_balacc_block_slopes, echo=FALSE, results='asis'}
kable(test(ncomorbid_BalAccInt_slopes), digits = 3, caption = "Nback nComorbid x Percent of Overweight: Balanced Accuracy simple slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
After controlling for Load, there was a significant interaction between percent of overweight and number of comorbidities such that the association between percent of overweight and balanced accuracy becomes more negative with increasing number of comorbidities. With zero comorbidities there was a significant positive association such that if percent of overweight increased by 10, ballanced accuracy is expected to increased by almost 1 percent (0.9). There was not a significant association for those with 1 or 2 comorbidities but a trend for a negative association for those with 3 comorbidities such that if percent of overweight increased by 10, balanced accuracy would be expected to decrease by almost 1 percent (0.7). There was a significant effect of Load with better balanced accuracy in 1- than 2-back. Age was positively associated with balanced accuracy overall.

\FloatBarrier

```{r pOW_nocomorbid_IQ70_balacc_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_IQg70_BalAccInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Ballanced Accuracy - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### False Alarms
\FloatBarrier

```{r pOW_ncomorbid_pFA_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_pFAInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Percent False Alarm", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
After controlling for Load, there was no  interaction between percent of overweight and number of comorbidities. There was a significant effect of Load with better balanced accuracy in 1- than 2-back. Age was positively associated with balanced accuracy overall.

\FloatBarrier

```{r pOW_ncomorbid_IQ70_pFA_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_IQg70_pFAInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Percent Hits
\FloatBarrier
```{r pOW_ncomorbid_phit_fig, echo=FALSE, include = TRUE}
pOW_ncomorbid_phit_plot
```
\FloatBarrier

```{r pOW_ncomorbid_phit_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_hitInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r pOW_ncomorbid_phit_block_slopes, echo=FALSE, results='asis'}
kable(test(ncomorbid_hitInt_slopes), digits = 3, caption = "Nback nComorbid x Percent of Overweight: Percent Hits simple slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r pOW_ncomorbid_IQ70_phit_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_IQg70_hitInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: Percent Hits - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### RT
\FloatBarrier

```{r pOW_ncomorbid_RT_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_meanRTInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: mean RT", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
After controlling for Load, there was no  interaction between percent of overweight and number of comorbidities. There was a significant effect of Load with better balanced accuracy in 1- than 2-back. Age was positively associated with balanced accuracy overall.

\FloatBarrier

```{r pOW_ncomorbid_IQ70_RT_block_mod, echo=FALSE, results='asis'}
kable(ncomorbid_IQg70_meanRTInt_sum$coefficients, digits = 3, caption = "Nback nComorbid x Percent of Overweight: mean RT - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

## Nback: Percent of Overweight x Sleep

### Balanced Accuracy

\FloatBarrier

```{r pOW_sleep_balacc_block_mod, echo=FALSE, results='asis'}
kable(sleep_BalAccInt_sum$coefficients, digits = 3, caption = "Nback CSHQ Total x Percent of Overweight: Ballanced Accuracy", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
There was no interaction between percent of overweight and total CSHQ score. There was a significant effect of Load with better balanced accuracy in 1- than 2-back. Age was positively associated with balanced accuracy overall.

\FloatBarrier

```{r pOW_sleep_IQ70_balacc_block_mod, echo=FALSE, results='asis'}
kable(sleep_IQg70_BalAccInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Ballanced Accuracy - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### False Alarms
\FloatBarrier
```{r pOW_sleep_pFA_fig, echo=FALSE, include = TRUE}
pOW_sleep_pFA_plot
```
\FloatBarrier

```{r pOW_sleep_pFA_block_mod, echo=FALSE, results='asis'}
kable(sleep_pFAInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r pOW_sleep_pFA_block_slopes, echo=FALSE, results='asis'}
kable(test(sleep_pFAInt_slopes), digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms simple slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
After controlling for Load, there was a significant interaction between percent of overweight and CSHQ Total score such that the association between percent of overweight and percent False Alarms becomes more negative with increasing sleep score (worse). There was a significant negative association between percent of overweight and percent false alarms when sleep was 1 SD lower than average, no association at average sleep score, and a significant negative association when sleep scores were 1 SD greater than average. When sleep was 1 SD below average, if percent of overweight increased by 10, false alarms are expected to be 1 percent lower (0.9). At 1 SD above the mean, if percent of overweight increased by 10, false alarms would be expected to be  almost 1 percent (0.9) higher.

\FloatBarrier

```{r pOW_sleep_no109_pFA_block_mod, echo=FALSE, results='asis'}
kable(sleep_no109_pFAInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms - no outlier", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when removing outlier.

\FloatBarrier

```{r pOW_sleep_IQ70_pFA_block_mod, echo=FALSE, results='asis'}
kable(sleep_IQg70_pFAInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Percent Hits 
\FloatBarrier

```{r pOW_sleep_phit_block_mod, echo=FALSE, results='asis'}
kable(sleep_hitInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier
After controlling for Load, there no interaction between percent of overweight and CSHQ Total score. 

\FloatBarrier

```{r pOW_sleep_IQ70_phit_block_mod, echo=FALSE, results='asis'}
kable(sleep_IQg70_hitInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### RT

\FloatBarrier

```{r pOW_Sleep_RT_block_mod, echo=FALSE, results='asis'}
kable(sleep_meanRTInt_sum$coefficients, digits = 3, caption = "Nback Sleep Total Problems x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier
After controlling for Load, there no interaction between percent of overweight and Sleep Total Problems. 

\FloatBarrier

```{r pOW_Sleep_IQ70_RT_block_mod, echo=FALSE, results='asis'}
kable(sleep_IQg70_meanRTInt_sum$coefficients, digits = 3, caption = "Nback Sleep Total Problems x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

## Nback: Percent of Overweight x SDQ

### Balanced Accuracy

\FloatBarrier

```{r pOW_SDQ_balacc_block_mod, echo=FALSE, results='asis'}
kable(SDQ_BalAccInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Ballanced Accuracy", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
There was no interaction between percent of overweight and SDQ total problems score. There was a significant effect of Load with better balanced accuracy in 1- than 2-back. Age was positively associated with balanced accuracy overall.

\FloatBarrier

```{r pOW_SDQ_IQ70_balacc_block_mod, echo=FALSE, results='asis'}
kable(SDQ_IQg70_BalAccInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Ballanced Accuracy - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### False Alarms

\FloatBarrier
```{r pOW_SDQ_pFA_fig, echo=FALSE, include = TRUE}
pOW_SDQ_pFA_plot
```
\FloatBarrier

```{r pOW_SDQ_pFA_block_mod, echo=FALSE, results='asis'}
kable(SDQ_pFAInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent False Alarms", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r pOW_SDQ_pFA_block_slopes, echo=FALSE, results='asis'}
kable(test(SDQ_pFAInt_slopes), digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent False Alarms simple slopes", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
After controlling for Load, there was a significant interaction between percent of overweight and SDQ Total Problems such that the association between percent of overweight and percent False Alarms becomes more positive with increasing total problems. At 1SD below the mean and meal Total Problems, the association between percent of overweight and percent false alarms was not significant. At 1 SD above the mean total problems, the association between percent of overweight and false alarms was significant. For a child who was 10 points higher on percent of overweight, it would be expected that they would have 0.6 percentage points higher false alarm rate.

\FloatBarrier

```{r pOW_SDQ_no109_pFA_block_mod, echo=FALSE, results='asis'}
kable(SDQ_no109_pFAInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms - no outlier", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
The interaction was no longer significant after removing the outliers.

\FloatBarrier

```{r pOW_SDQ_IQ70_pFA_block_mod, echo=FALSE, results='asis'}
kable(SDQ_IQg70_pFAInt_sum$coefficients, digits = 3, caption = "Nback CSHQ x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### Percent Hits

\FloatBarrier

```{r pOW_SDQ_phit_block_mod, echo=FALSE, results='asis'}
kable(SDQ_hitInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier
After controlling for Load, there no interaction between percent of overweight and SDQ Total Problems. 

\FloatBarrier

```{r pOW_SDQ_IQ70_phit_block_mod, echo=FALSE, results='asis'}
kable(SDQ_IQg70_hitInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

### RT

\FloatBarrier

```{r pOW_SDQ_RT_block_mod, echo=FALSE, results='asis'}
kable(SDQ_meanRTInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent Hits", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier
After controlling for Load, there no interaction between percent of overweight and SDQ Total Problems. 

\FloatBarrier

```{r pOW_SDQ_IQ70_RT_block_mod, echo=FALSE, results='asis'}
kable(SDQ_IQg70_meanRTInt_sum$coefficients, digits = 3, caption = "Nback SDQ Total Problems x Percent of Overweight: Percent False Alarms - IQ >=70 ", booktabs=TRUE)  %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
Pattern of results remained unchanged when restricting to IQ >=70.

\FloatBarrier

